Towards Bridging the Gap... [TBD]

### 2014-03-13 paper/draft.tex
First commit...

\documentclass{acm_proc_article-sp} % use larger type; default would be 10pt
%\usepackage[margin={1.5cm,3cm}]{geometry}
%\setlength{\columnsep}{1cm}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

@@

%%% PAGE DIMENSIONS
%\usepackage{geometry} % to change the page dimensions
%\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
\usepackage[hidelinks]{hyperref}
\usepackage[autostyle,french=guillemets,babel]{csquotes}
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage[backend=biber]{biblatex}
\addbibresource{biblio.bib}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} %
% for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsfonts}

@@

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\numberofauthors{1}
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed 
}

%\setlist[itemize]{leftmargin=*}
\begin{document}
\maketitle

\abstract{
%Today, hypervisors have to find a complex trade-off between functionalities provided and security assurance. Those requirements are contrasting by design:
%adding new features will generally increases the LoC and consequently the attack surface. On the contrary, those code additions are required to properly fulfill market requests. 
%
%Nested virtualization is a technique capable to diversify hypervisor features. Exploiting an extra layer of virtualization, we will be able to decouple different requirements, avoiding the need to find delicate trade-off.
%
%In this paper, we will analyze the state of nested virtualization in modern hypervisor and evaulating the impact of utilization of microhypervisor to enforce a stronger security level.

}

@@

\begin{figure}
\caption{Xen over NOVA architecture}
\label{fig:io}
\begin{center}
\includegraphics[width=0.6\columnwidth]{article.png}
\end{center}
\end{figure}

@@

%\section{Conclusion}
\printbibliography
\end{document}

>>>>

\documentclass{sig-alternate}
%\usepackage[margin={1.5cm,3cm}]{geometry}
%\setlength{\columnsep}{1cm}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

@@

%%% PAGE DIMENSIONS
%\usepackage{geometry} % to change the page dimensions
%\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
%\usepackage[hidelinks]{hyperref}
%\usepackage[autostyle,french=guillemets,babel]{csquotes}
\usepackage{graphicx} % support the \includegraphics command and options
%\usepackage[backend=biber]{biblatex}
%\addbibresource{biblio.bib}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} %
% for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
%\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsfonts}

@@

\title{Towards Bridging the Gap... [TBD]}

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\numberofauthors{3}
\alignauthor
Alex Palesandro\\
\affaddr{Orange Labs, France}\\
\texttt{palexster@gmail.com}
\alignauthor
Aurélien Wailly\\
\affaddr{Orange Labs, France}\\
\texttt{aurelien.wailly@orange.com}
\alignauthor
Marc Lacoste\\
\affaddr{Orange Labs, France}
\texttt{marc.lacoste@orange.com}
}
%\setlist[itemize]{leftmargin=*}
\begin{document}
\maketitle

\abstract{
%Today, hypervisors have to find a complex trade-off between functionalities provided and security assurance. Those requirements are contrasting by design:
%adding new features will generally increases the LoC and consequently the attack surface. On the contrary, those code additions are required to properly fulfill market requests. 
%
%Nested virtualization is a technique capable to diversify hypervisor features. Exploiting an extra layer of virtualization, we will be able to decouple different requirements, avoiding the need to find delicate trade-off.
%
%In this paper, we will analyze the state of nested virtualization in modern hypervisor and evaulating the impact of utilization of microhypervisor to enforce a stronger security level.
}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.6\columnwidth]{article.png}
\end{center}
\caption{Xen over NOVA architecture}
\label{fig:io}
\end{figure}

@@

%\section{Conclusion}
%{\scriptsize
%\bibliographystyle{abbrv}
%\bibliography{biblio}
%}
\end{document}
